\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-08-05 paper/paper.tex
Updates.

Our evaluation has, thus far, focused on synthetic write heavy
workloads. To illustrate that Cyclone can also be useful for read-heavy
workloads, we configured our clients to generate key value requests that mimic
the distribution of value sizes in Facebook's ETCD
trace~\cite{fb_workload_analysis,fb_scaling_memcache} and are read
heavy (95\% reads). Figure~\ref{fig:fb} illustrates that even with a
read-dominated workload, Cyclone is effective at providing a write ahead log
with 3 way replication with a lower performance overhead than Rocksdb's own
write ahead logging.

@@

>>>>

Our evaluation has, thus far, focused on synthetic write heavy
workloads. To illustrate that Cyclone can also be useful for read-heavy
workloads, we configured our clients to generate key value requests that mimic
the distribution of value sizes in Facebook's ETCD
trace~\cite{fb_workload_analysis,fb_scaling_memcache} and are read
heavy (95\% reads). Figure~\ref{fig:fb} illustrates that even with a
read-dominated workload, Cyclone is effective at providing a write ahead log
with 3 way replication with a lower performance overhead than Rocksdb's own
write ahead logging. We consider the case of a workload that more write
intensive at 80\% writes with a smaller range of value sizes, derived from
Facebook's VAR trace~~\cite{fb_workload_analysis,fb_scaling_memcache}, in
Figure~\ref{fig:fb2}. One can similarly conclude that Cyclone provides more
functionality (replicated write ahead log) at a far lower performance penalty
that Rocksdb's existing single machine write ahead log solution.

@@

\begin{figure}
  \includegraphics[scale=0.6]{results2/fb2.pdf}
\caption{Rocksdb - write heavy workload}
\label{fig:fb2}
\end{figure}
